Emory Cardiovscular Biobank

### 2021-06-01 Real_Data/Emory_Card_Biobank/Report.Rmd
Addeing split validation in the model

# Primary Data Analysis of Metabolites

>>>>

## Primary Data Analysis of Metabolites
```{r eval=F}
train_dat %>% select(starts_with("mz")) %>% 
  summarise_all(var)
```

# Predictive Model

Outcome: `death3yr` (bin)
Covariates: None
Predictors: `starts_with("mz")`

```{r data_split}
library(tidymodels)

set.seed(1)

data_split <- rsample::initial_split(train_dat, prop = 3/4)

train_data <- training(data_split)
test_data <- testing(data_split)
```

## Baseline: Linear Lasso Model

```{r}
library(glmnet)

lasso_mdl_cv <- cv.glmnet(x = train_data %>% select(starts_with("mz")) %>% data.matrix,
                    y = train_data %>% pull(death3yr), alpha = 1,
                    family = "binomial", type.measure = "auc")

lasso_mdl <- glmNet(x = train_data %>% select(starts_with("mz")) %>% data.matrix,
                    y = train_data %>% pull(death3yr), alpha = 1,
                    family = "binomial",lambda = lasso_mdl_cv$lambda.1se)

# class(lasso_mdl) <- c("glmNet", class(lasso_mdl))
measure.bh(lasso_mdl)
# assess.glmnet(lasso_mdl$)

measure.bh(lasso_mdl, new.x = test_data %>% select(starts_with("mz")) %>% data.matrix,
           new.y = test_data %>% pull(death3yr))
```

```{r}
library(BHAM)
library(BhGLM)

mz_names <- train_dat %>% select(starts_with("mz")) %>% names  
sm_df <- data.frame(
  Var = mz_names,
 Func = "s",
 Args ="bs='cr', k=5"
)

sm_obj <- construct_smooth_data(sm_df, train_data)

dsn_mat <- sm_obj$data

# The validation data doesn't overlap with training data
# test_sm_dat <- make_predict_dat(sm_obj$Smooth, dat = valid_dat)

mdl_defaul <- bmlasso(dsn_mat, train_data$death3yr, family = "binomial")

mdl_dflt <- bmlasso_spline(dsn_mat, train_data$death3yr, family = "binomial",
                           group = make_group(names(dsn_mat)))

# Training Data Performance
measure.bh(mdl_defaul)
measure.bh(mdl_dflt)

test_sm_dat <- BHAM::make_predict_dat(sm_obj$Smooth, dat=test_data)

# Testing Data Performance
measure.bh(mdl_defaul, new.x = test_sm_dat, new.y=test_data$death3yr)
measure.bh(mdl_dflt, new.x = test_sm_dat, new.y=test_data$death3yr)
```

# Extremely Penalized Model
```{r}

mdl_pen_extreme <- bmlasso_spline(dsn_mat, train_data$death3yr, family = "binomial",
                           group = make_group(names(dsn_mat)),
                           ss = c(0.001, 0.5))

# Training Data Performance
measure.bh(mdl_pen_extreme)

# Testing Data Performance
measure.bh(mdl_pen_extreme, new.x = test_sm_dat, new.y=test_data$death3yr)
```

## Validation

The validation data set have mostly distinct feature from the training data set. Hence, the validation in the traditional sense does not exists.

```{r eval = F}

test_mz_names <- valid_dat  %>% select(starts_with("mz")) %>% names
measure.bh(mdl_defaul, new.x = test_sm_dat, new.y=valid_dat$death3yr)

measure.bh(mdl_dflt)
```
